Market simulator

### 2020-09-16 analysis/05_market_simulator.Rmd
Still cleaning up and looking for errors

```{r load-data}
# Gammas of the "everything" model
public_political_social_charity_demo <- read_rds(here::here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')) %>% 
  group_by(i, j) %>% 
  summarize(gamma_mean = mean(Gamma)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = j, values_from = gamma_mean) %>% 
  select(-i) %>% 
  t()

# Starting organization configuration
organization_data <- read_csv(here::here('analysis', 'output', 'configurations', 'organization_config01.csv'))

# Starting persona configuration
persona_data <- read_csv(here::here('analysis', 'output', 'configurations', 'persona_config01.csv'))
```

```{r organization-reactive-table}
# Placeholder for organization gammas
gamma <- as.data.frame(matrix(rep(0), nrow = 13))

# Assign level labels
gamma$levels = c(
  # Organization
  "Amnesty International",
  "Greenpeace", 
  "Oxfam", 
  "Red Cross",
  # Issue Area
  "Environment", 
  "Human rights",
  "Refugee relief",
  # Financial Transparency
  "Engages in financial transparency",
  # Financial Accountability
  "Engages in financial accountability",
  # Funding Sourcs
  "Handful of wealthy private donors", 
  "Government grants",
  # Relationship with Host Government
  "Criticized by government",
  "Under government crackdown"
)

# Organization configuration reactive element
df <- reactive({

  # Amnesty International
    gamma$ai_value <- 0
    gamma$ai_value[gamma$levels %in% input$org1_id] <- 1
    gamma$ai_value[gamma$levels %in% input$ai_issue] <- 1
    gamma$ai_value[gamma$levels %in% input$ai_fin_trans] <- 1
    gamma$ai_value[gamma$levels %in% input$ai_account] <- 1
    gamma$ai_value[gamma$levels %in% input$ai_funding] <- 1
    gamma$ai_value[gamma$levels %in% input$ai_gov_relat] <- 1

  #Greenpeace
    gamma$gp_value <- 0
    # gamma$gp_value[gamma$levels == 'Greenpeace'] <- 1
    gamma$gp_value[gamma$levels %in% input$org2_id] <- 1
    gamma$gp_value[gamma$levels %in% input$gp_issue] <- 1
    gamma$gp_value[gamma$levels %in% input$gp_fin_trans] <- 1
    gamma$gp_value[gamma$levels %in% input$gp_account] <- 1
    gamma$gp_value[gamma$levels %in% input$gp_funding] <- 1
    gamma$gp_value[gamma$levels %in% input$gp_gov_relat] <- 1

  #Oxfam
    gamma$ox_value <- 0
    # gamma$ox_value[gamma$levels == 'Oxfam'] <- 1
    gamma$ox_value[gamma$levels %in% input$org3_id] <- 1
    gamma$ox_value[gamma$levels %in% input$ox_issue] <- 1
    gamma$ox_value[gamma$levels %in% input$ox_fin_trans] <- 1
    gamma$ox_value[gamma$levels %in% input$ox_account] <- 1
    gamma$ox_value[gamma$levels %in% input$ox_funding] <- 1
    gamma$ox_value[gamma$levels %in% input$ox_gov_relat] <- 1

  #Redcross
    gamma$rc_value <- 0
    # gamma$rc_value[gamma$levels == 'Red Cross'] <- 1
    gamma$rc_value[gamma$levels %in% input$org4_id] <- 1
    gamma$rc_value[gamma$levels %in% input$rc_issue] <- 1
    gamma$rc_value[gamma$levels %in% input$rc_fin_trans] <- 1
    gamma$rc_value[gamma$levels %in% input$rc_account] <- 1
    gamma$rc_value[gamma$levels %in% input$rc_funding] <- 1
    gamma$rc_value[gamma$levels %in% input$rc_gov_relat] <- 1
    gamma

})
```

```{r persona-reactive-table}
# Placeholder for persona gammas
gamma_persona <- as.data.frame(matrix(rep(0), nrow = 111))

# Assign covariate labels
gamma_persona$levels <- c(
  "Intercept",
  # Follow national news
  "Once a week",
  "At least once a day",
  # Follow international news
  "Sometimes",
  "Always",
  # Mediums to follow news
  "TV",
  "Print",
  "Online (not social media)",
  "Social media",
  "Radio",
  "Email newsletter",
  "News app",
  # Follow government and public affairs
  "Often", 
  # Traveled to a developing country
  "Traveled to a developing country", 
  # Liberal to Conservative
  "Somewhat liberal",
  "Slightly liberal",
  "Moderate",
  "Slightly conservative",
  "Somewhat conservative",
  "Extremely conservative",
  # Trust in political institutions
  "Very little trust in political institutions",
  "Little trust in political institutions",
  "Neutral trust in political institutions",
  "Some trust in political institutions",
  "A lot of trust in political institutions",
  "Complete trust in political institutions",
  # People should be more charitable
  "Disagree",
  "Somewhat disagree",
  "Neutral",
  "Somewhat agree",
  "Agree",
  "Strongly agree",
  # Religious attendance
  "Rarely attend",
  "Attend at least once a month",
  # Importance of religion
  "Important",
  # Religion
  "Protestant",
  "Christian Orthodox",
  "Jewish",
  "Muslim",
  "Sikh",
  "Hindu",
  "Buddhist",
  "Atheist",
  "Other religion",
  # Importance of trusing charities
  "Very unimportant",
  "Somewhat unimportant",
  "Neutral",
  "Somewhat important",
  "Very important",
  "Essential",
  # Trust in charities
  "Very little trust in charities",
  "Little trust in charities",
  "Neutral trust in charities",
  "Some trust in charities",
  "A lot of trust in charities",
  "Complete trust in charities",
  # Donation frequency
  "Donate at least once a month", 
  # Donated last year
  "$50-$99",
  "$100-$499",
  "$500-$999",
  "$1,000-$4,999",
  "$5,000-$9,999",
  "$10,000 +",
  # Volunteered in past 12 months
  "Volunteered in past 12 months",
  # Volunteer frequency
  "Rarely volunteer",
  "Volunteer more than once a month, less than once a year",
  "Volunteer at least once a month",
  # History of activism
  "Personally involved",
  # History of family activism
  "Family involved",
  # Church or religious organization
  "Inactive church member",
  "Active church member",
  # Sport or recreational organization
  "Inactive sports or rec organization member",
  "Active sports or rec organization member", 
  # Art, music, or educational organization
  "Inactive art, music, or educational organization member",
  "Active art, music, or educational organization member",
  # Labor union
  "Inactive union member",
  "Active union member",
  # Political party
  "Inactive political party member",
  "Active political party member",
  # Environmental organization
  "Inactive environmental organization member",
  "Active environmental organization member",
  # Professional association
  "Inactive professional association member",
  "Active professional association member",
  # Humanitarian or charitable organization
  "Inactive humanitarian or charitable organization member",
  "Active humanitarian or charitable organization member",
  # Consumer organization
  "Inactive consumer organization member",
  "Active consumer organization member",
  # Other organization
  "Inactive member in another organization",
  "Active member in another organization",
  # Gender
  "Female",
  "Transgender",
  "Prefer not to say",
  "Other gender",
  # Marital status
  "Widowed",
  "Divorced",
  "Separated",
  "Never married",
  # Education
  "High school graduate", 
  "Some college",
  "2 year degree",
  "4 year degree",
  "Graduate or professional degree",
  "Doctorate",
  # Income
  "More than median of $61,372", 
  # Race
  "White", 
  "Black or African American", 
  "American Indian or Alaskan Native", 
  "Asian", 
  "Native Hawaiian or Pacific Islander",
  "Other race",
  # Age
  "More than median age of 36"
)

# p reactive element ----

p <- reactive({

  #Persona 1
    gamma_persona$p1_value <- 0

    gamma_persona$p1_value[gamma_persona$levels == 'Intercept'] <- 1

    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_national_news] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_international_news] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_news_medium] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_follow_gov] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_travel_developing] <- 1

    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_political_pref] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_institution_trust] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_others_charitable] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_worship_attendence] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_religion_importance] <- 1

    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_religion] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_charity_importance] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_trust_in_charity] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_donation_frequency] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_donation_amount] <- 1

    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_volunteer_12] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_volunteer_frequency] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_personal_activism] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_family_activism] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_religious_member] <- 1

    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_sport_member] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_art_member] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_labor_member] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_political_member] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_environmental_member] <- 1

    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_professional_member] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_humanitarian_member] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_consumer_member] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_other_member] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_gender] <- 1

    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_marital_status] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_education] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_income] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_race] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_age] <- 1

  #Persona 2
    gamma_persona$p2_value <- 0

    gamma_persona$p2_value[gamma_persona$levels == 'Intercept'] <- 1

    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_national_news] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_international_news] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_news_medium] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_follow_gov] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_travel_developing] <- 1

    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_political_pref] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_institution_trust] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_others_charitable] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_worship_attendence] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_religion_importance] <- 1

    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_religion] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_charity_importance] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_trust_in_charity] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_donation_frequency] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_donation_amount] <- 1

    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_volunteer_12] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_volunteer_frequency] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_personal_activism] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_family_activism] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_religious_member] <- 1

    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_sport_member] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_art_member] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_labor_member] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_political_member] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_environmental_member] <- 1

    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_professional_member] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_humanitarian_member] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_consumer_member] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_other_member] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_gender] <- 1

    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_marital_status] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_education] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_income] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_race] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_age] <- 1

  #Persona 3
    gamma_persona$p3_value <- 0

    gamma_persona$p3_value[gamma_persona$levels == 'Intercept'] <- 1

    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_national_news] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_international_news] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_news_medium] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_follow_gov] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_travel_developing] <- 1

    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_political_pref] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_institution_trust] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_others_charitable] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_worship_attendence] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_religion_importance] <- 1

    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_religion] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_charity_importance] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_trust_in_charity] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_donation_frequency] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_donation_amount] <- 1

    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_volunteer_12] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_volunteer_frequency] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_personal_activism] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_family_activism] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_religious_member] <- 1

    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_sport_member] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_art_member] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_labor_member] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_political_member] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_environmental_member] <- 1

    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_professional_member] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_humanitarian_member] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_consumer_member] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_other_member] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_gender] <- 1

    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_marital_status] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_education] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_income] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_race] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_age] <- 1
    gamma_persona

})

@@

```{r practice-code}

# this chunk is for testing code and making sure things work before adding it into the dashboard

# df <- as.data.frame(matrix(rep(0), nrow = 1))
# 
# df$levels = "Rating"
#                         
#                         
# df$p1[df$levels == "Rating"] <- input$rating_id
# 
# 
# p1_pol_pref <- reactive({
#   input$p1_political_pref
# })
# 
# 
# sliderInput("rating_id",
#        label = "Rating",
#        min = 0,
#        max = 7,
#        value = 0)

>>>>

```{r load-data}
# Gammas of the "everything" model
public_political_social_charity_demo <- read_rds(
  here::here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')
  ) %>% 
  group_by(i, j) %>% 
  summarize(gamma_mean = mean(Gamma)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = j, values_from = gamma_mean) %>% 
  select(-i) %>% 
  t()

# Initial organization configuration
organization_data <- read_csv(
  here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
)

# Initial persona configuration
persona_data <- read_csv(
  here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
)
```

```{r organization-reactive-table}
# Placeholder for organization reactive table
org_table <- as.data.frame(matrix(rep(0), nrow = nrow(organization_data)))

# Assign level labels
org_table$levels = c(
  # Organization
  "Amnesty International",
  "Greenpeace", 
  "Oxfam", 
  "Red Cross",
  # Issue area
  "Environment", 
  "Human rights",
  "Refugee relief",
  # Financial transparency
  "Engages in financial transparency",
  # Financial accountability
  "Engages in financial accountability",
  # Funding sources
  "Handful of wealthy private donors", 
  "Government grants",
  # Relationship with host government
  "Criticized by government",
  "Under government crackdown"
)

# Organization configuration reactive element
org_reactive <- reactive({
  # Organization 1
  org_table$org1_value <- 0
  org_table$org1_value[org_table$levels %in% input$org1_id] <- 1
  org_table$org1_value[org_table$levels %in% input$org1_issue] <- 1
  org_table$org1_value[org_table$levels %in% input$org1_fin_trans] <- 1
  org_table$org1_value[org_table$levels %in% input$org1_fin_account] <- 1
  org_table$org1_value[org_table$levels %in% input$org1_funding] <- 1
  org_table$org1_value[org_table$levels %in% input$org1_host_gov] <- 1

  # Organization 2
  org_table$org2_value <- 0
  org_table$org2_value[org_table$levels %in% input$org2_id] <- 1
  org_table$org2_value[org_table$levels %in% input$org2_issue] <- 1
  org_table$org2_value[org_table$levels %in% input$org2_fin_trans] <- 1
  org_table$org2_value[org_table$levels %in% input$org2_fin_account] <- 1
  org_table$org2_value[org_table$levels %in% input$org2_funding] <- 1
  org_table$org2_value[org_table$levels %in% input$org2_host_gov] <- 1

  # Organization 3
  org_table$org3_value <- 0
  org_table$org3_value[org_table$levels %in% input$org3_id] <- 1
  org_table$org3_value[org_table$levels %in% input$org3_issue] <- 1
  org_table$org3_value[org_table$levels %in% input$org3_fin_trans] <- 1
  org_table$org3_value[org_table$levels %in% input$org3_fin_account] <- 1
  org_table$org3_value[org_table$levels %in% input$org3_funding] <- 1
  org_table$org3_value[org_table$levels %in% input$org3_host_gov] <- 1

  # Organization 4
  org_table$org4_value <- 0
  org_table$org4_value[org_table$levels %in% input$org4_id] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_issue] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_fin_trans] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_fin_account] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_funding] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_host_gov] <- 1
  org_table
})
```

```{r persona-reactive-table}
# Placeholder for persona gammas
per_table <- as.data.frame(matrix(rep(0), nrow = 111))

# Assign covariate labels
per_table$levels <- c(
  # Intercept
  "Intercept",
  # Follow national news
  "Once a week",
  "At least once a day",
  # Follow international news
  "Sometimes",
  "Always",
  # Mediums to follow news
  "TV",
  "Print",
  "Online (not social media)",
  "Social media",
  "Radio",
  "Email newsletter",
  "News app",
  # Follow government and public affairs
  "Often", 
  # Traveled to a developing country
  "Traveled to a developing country", 
  # Liberal to Conservative
  "Somewhat liberal",
  "Slightly liberal",
  "Moderate",
  "Slightly conservative",
  "Somewhat conservative",
  "Extremely conservative",
  # Trust in political institutions
  "Very little trust in political institutions",
  "Little trust in political institutions",
  "Neutral trust in political institutions",
  "Some trust in political institutions",
  "A lot of trust in political institutions",
  "Complete trust in political institutions",
  # People should be more charitable
  "Disagree",
  "Somewhat disagree",
  "Neutral",
  "Somewhat agree",
  "Agree",
  "Strongly agree",
  # Religious attendance
  "Rarely attend",
  "Attend at least once a month",
  # Importance of religion
  "Important",
  # Religion
  "Protestant",
  "Christian Orthodox",
  "Jewish",
  "Muslim",
  "Sikh",
  "Hindu",
  "Buddhist",
  "Atheist",
  "Other religion",
  # Importance of trusing charities
  "Very unimportant",
  "Somewhat unimportant",
  "Neutral",
  "Somewhat important",
  "Very important",
  "Essential",
  # Trust in charities
  "Very little trust in charities",
  "Little trust in charities",
  "Neutral trust in charities",
  "Some trust in charities",
  "A lot of trust in charities",
  "Complete trust in charities",
  # Donation frequency
  "Donate at least once a month", 
  # Donated last year
  "$50-$99",
  "$100-$499",
  "$500-$999",
  "$1,000-$4,999",
  "$5,000-$9,999",
  "$10,000 +",
  # Volunteered in past 12 months
  "Volunteered in past 12 months",
  # Volunteer frequency
  "Rarely volunteer",
  "Volunteer more than once a month, less than once a year",
  "Volunteer at least once a month",
  # History of activism
  "Personally involved",
  # History of family activism
  "Family involved",
  # Church or religious organization
  "Inactive church member",
  "Active church member",
  # Sport or recreational organization
  "Inactive sports or rec organization member",
  "Active sports or rec organization member", 
  # Art, music, or educational organization
  "Inactive art, music, or educational organization member",
  "Active art, music, or educational organization member",
  # Labor union
  "Inactive union member",
  "Active union member",
  # Political party
  "Inactive political party member",
  "Active political party member",
  # Environmental organization
  "Inactive environmental organization member",
  "Active environmental organization member",
  # Professional association
  "Inactive professional association member",
  "Active professional association member",
  # Humanitarian or charitable organization
  "Inactive humanitarian or charitable organization member",
  "Active humanitarian or charitable organization member",
  # Consumer organization
  "Inactive consumer organization member",
  "Active consumer organization member",
  # Other organization
  "Inactive member in another organization",
  "Active member in another organization",
  # Gender
  "Female",
  "Transgender",
  "Prefer not to say",
  "Other gender",
  # Marital status
  "Widowed",
  "Divorced",
  "Separated",
  "Never married",
  # Education
  "High school graduate", 
  "Some college",
  "2 year degree",
  "4 year degree",
  "Graduate or professional degree",
  "Doctorate",
  # Income
  "More than median of $61,372", 
  # Race
  "White", 
  "Black or African American", 
  "American Indian or Alaskan Native", 
  "Asian", 
  "Native Hawaiian or Pacific Islander",
  "Other race",
  # Age
  "More than median age of 36"
)

# Persona configuration reactive element
per_reactive <- reactive({
  # Persona 1
  per_table$per1_value <- 0
  per_table$per1_value[per_table$levels == 'Intercept'] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_national_news] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_international_news] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_news_medium] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_follow_gov] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_travel_developing] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_political_pref] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_institution_trust] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_others_charitable] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_worship_attendence] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_religion_importance] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_religion] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_charity_importance] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_trust_in_charity] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_donation_frequency] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_donation_amount] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_volunteer_12] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_volunteer_frequency] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_personal_activism] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_family_activism] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_religious_member] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_sport_member] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_art_member] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_labor_member] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_political_member] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_environmental_member] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_professional_member] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_humanitarian_member] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_consumer_member] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_other_member] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_gender] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_marital_status] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_education] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_income] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_race] <- 1
  per_table$per1_value[per_table$levels %in% input$per1_age] <- 1

  # Persona 2
  per_table$per2_value <- 0
  per_table$per2_value[per_table$levels == 'Intercept'] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_national_news] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_international_news] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_news_medium] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_follow_gov] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_travel_developing] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_political_pref] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_institution_trust] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_others_charitable] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_worship_attendence] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_religion_importance] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_religion] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_charity_importance] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_trust_in_charity] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_donation_frequency] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_donation_amount] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_volunteer_12] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_volunteer_frequency] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_personal_activism] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_family_activism] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_religious_member] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_sport_member] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_art_member] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_labor_member] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_political_member] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_environmental_member] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_professional_member] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_humanitarian_member] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_consumer_member] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_other_member] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_gender] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_marital_status] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_education] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_income] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_race] <- 1
  per_table$per2_value[per_table$levels %in% input$per2_age] <- 1

  # Persona 3
  per_table$per3_value <- 0
  per_table$per3_value[per_table$levels == 'Intercept'] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_national_news] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_international_news] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_news_medium] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_follow_gov] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_travel_developing] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_political_pref] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_institution_trust] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_others_charitable] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_worship_attendence] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_religion_importance] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_religion] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_charity_importance] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_trust_in_charity] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_donation_frequency] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_donation_amount] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_volunteer_12] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_volunteer_frequency] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_personal_activism] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_family_activism] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_religious_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_sport_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_art_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_labor_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_political_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_environmental_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_professional_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_humanitarian_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_consumer_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_other_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_gender] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_marital_status] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_education] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_income] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_race] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_age] <- 1
  per_table
})

@@

```{r matrix-multiplication, eval=FALSE, include=FALSE}
# # Overwrite gamma??
# gamma <- data.frame(
#   value = c(0,0,0),
#   levels = c("Environment", "Human rights", "Refugee relief")
# )
# 
# ui <- fluidPage(
#   fluidRow(
#     column(6,
#       selectInput("org1_issue", 
#                   label = "Select Issue Area:",
#                   choices = gamma$levels,
#                   multiple = TRUE)
#     ),
#     column(6,
#       tableOutput("data")
#     )
#   )
# )
# 
# server = function(input, output) {
#   org_reactive <- reactive({
#     gamma$value[gamma$levels %in% input$org1_issue] <- 1
#     gamma
#   })
# 
#   output$data <- renderTable({
#     organizations()
#   })
# }
```

```{r Manual Testing Matrix Multiplication}
